{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2016-01-07 paper.tex
Remove Figures brackets and fix typo of reviewer 2

@@

For this shortening purpose, random shortcut (RS) methods are
still very 
popular~\cite{Sekhavat-Svestka1998,Geraerts04clearancebased,HauserFastSmooth}. 
However, RS requires fine 
tuning of the termination condition and is no efficient for long 
trajectories where only a minor part needs to be optimized, 
as in (Figure~\ref{local_box_optim}).
(Figure~\ref{decoupled_DOF_optimization}) presents another situation where RS 
will always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs. This problem is 
addressed by our method.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building. For example,~\cite{HauserFastSmooth} returns smooth shortcuts made of parabola and line combinations, relying on the classical bang-bang control approach. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
Also based on random shooting,~\cite{Guernane2011} is guiding 
configuration-generation with local holonomic considerations. 
Nevertheless this method remains only 
locally optimal, and is not addressing high-DOF 
problems.~\cite{Geraerts04clearancebased} is 
using medial axis retraction for clearance and a PRS (shortcut is applied only 
on some random DOF) 
which can address the problem of (Figure~\ref{decoupled_DOF_optimization}). 
However it is 
relatively slower than RS, and~\cite{Geraerts04clearancebased} only investigates 
it for freeflyer robots. 
Furthermore PRS is not taking advantage of information returned by 
the checker of which links are colliding, in order to guide the selection of a relevant group of DOF to shortcut.

In some way, our method shares similarities with~\cite{PanSmoothSplineShort} 
since this latter work relies on collision checking and backtracks when an 
iteration is detected in collision, instead of trying to constantly satisfy 
distance constraints. Unlike our method however, collision constraints are 
handled by interpolating configurations which, at some points of the trajectory, 
freeze the whole robot configuration instead of a pertinent subpart. Thus, this 
method cannot solve (Figure~\ref{decoupled_DOF_optimization}) issue.

@@

As illustrated in (Figure~\ref{optim_grad}), let 
us denote by $\tcolli$ the abscissa of the first collision detected on path 
$\xx_{i+1}$, which previous iteration $\xx_i$ was collision-free. Thus in 
configuration $\xx_{i+1}(\tcolli)$ a collision has been 
detected. Two cases are possible:
\begin{enumerate}
\item the collision occurred between two bodies of the robot: $\body_1$ and $
\body_2$, or
\item the collision occurred between a body of the robot $\body_1$ and the 
environment.
\end{enumerate}
In the rest of this section, the first case will only be considered. Reasoning 
about the second case is similar, except that the 
constraint is on the position of $\body_1$ with respect to the environment.

@@

Therefore the following expressions
% \frac{\partial \conf}{\partial t}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \text{and} \ \frac{\partial \conf}{\partial t}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
\dot{\conf}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \ \text{and} \ \ \dot{\conf}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
correspond to $(\dot{\po_2}|\mathbf{u})$, respectively in configurations $\xx_{i}(t_{coll\ i})$ and $\xx_{i+1}(t_{coll\ i})$. The term $\dot{\conf}(1)$ being equal to zero requires either:
\begin {enumerate}
\item that $\po_1$ and $\po_2$ come to contact at zero velocity, or
\item the velocity of $\po_2$ in the reference frame of $\body_1$ is orthogonal to 
$\mathbf{u}$ at contact ($t=1$).
\end {enumerate}
The first case is very unlikely and almost never encountered in real applications, 
except if the user builds such a case on purpose.
The second case may appear and can be noted by a rank loss of $\Jf_{i+1}$.
Then we do not directly insert the new constraint. Instead, we process intermediate 
iterations until the redundancy vanishes, as explained in function 
\texttt{findNewConstraint} in (Algorithm~\ref{algo:solveRedundant}), and illustrated in (Figure~\ref{fig:convergence-diagram}).

@@

(Figure~\ref{2D_long}) shows the result of our optimizer on 2D cases. Contact points which have 
led to constraints are represented. They permit to understand how the path is kept out of the obstacles. 
Unfortunately, it is not possible in the GB method to choose at which distance of the obstacle 
the constraint must be created, since at some parts the robot is very close to obstacles.

@@

(Figure~\ref{local_box_optim}) illustrates a \textit{very long} path example which RS 
or PRS will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. The GB method succeeds to optimize the 
path contained in the box, with the following cost coefficients:
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}, \  i \in [1\,..\, wp+1]  
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq wp+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated. This is not relevant for 
(Figure~\ref{local_box_optim}) type of problems where a local passage is very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper, and provides better quality results than the original cost.

@@

We also experiment our algorithm on more complex robots and environments.
In the included video and (Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}), we present multiple situations where the GB algorithm 
is tested and compared to RS~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}) and PRS~\cite{partialrandomShortcutHPP} 
adapted from~\cite{Geraerts04clearancebased}.
The termination condition of RS allows it to try 
shortening the path until five iterations of non-improvement are reached. 
This corresponds to $maxNbFailures$ in (Algorithm~\ref{algo:random-shortcut}).
For our implementation of PRS, first a shortcut is tried on each DOF between 
$\conf_0$ and $\conf_{wp+1}$. 
Then, for each DOF, configurations are sampled as in 
(Algorithm~\ref{algo:random-shortcut}). The steering-method returns a path made of 
an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, we replace it as in RS. This process is also stopped when five 
iterations of non-improvement are reached.

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to (Figure~\ref{fig:trajectories:puzzle}). The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
Lengths of initial, GB optimized, and RS optimized paths are 
respectively 23.4, 8.53 and 10.2. PRS fails to decrease the path length because in 
this problem, all DOF are closely related to cross the hole. This behavior was also 
noticed and improved in the PRS implementation of~\cite{Geraerts04clearancebased}, 
acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory 
even in the hole, contrary to RS which simply copies the initial path when the 
trajectory gets near of the obstacle. $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.

@@

% double-arm:
In the double-arm situation, (Figure~\ref{fig:trajectories:double_arm}), one arm has 
to get around a cylinder obstacle while the 
other arm is relatively far from obstacles. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Unlike RS, 
the GB optimizer manages to cancel the rotation of the free-arm while optimizing the 
first arm motion, even if the second arm is still moving because of the translation 
motion. The initial path length 5.17 is decreased to 4.55 by RS, to 4.06 by PRS and 
to 2.77 by the GB method using three collision-constraints with the cylinder obstacle.

@@

% UR5-spheres:
Some problems are 
involving a 6-axis manipulator arm, also called UR5, equipped with a bar or a 
gripper.
In a relatively free environment (Figure~\ref{fig:trajectories:ur5}), 
results from our method and RS are similar (path length are respectively 2.03 and 1.60). 
Note also that the end-effector trajectory is completely different from the initial 
one: the robot is easily passing between the spheres, keeping its end-effector 
above.

% UR5-fiad
For an UR5 working in a cluttered environment inspired by an industrial issue 
(Figure~\ref{fiad}), path optimization efficiently returns a shorter solution, close 
to the result of RS and to what can be observed in reality~\cite{factory-day-video}. 
The initial path length 6.65 is decreased to 2.08 by RS, to 
1.98 by the GB optimizer and unchanged by PRS.

% baxter:
A problem involving a Baxter-like\footnote{A torso rotation was added.} robot 
manipulating in an office environment is presented 
(Figure~\ref{fig:trajectories:baxter}). The robot starts with its end-effectors 
above the computer and has to 
turn and reach the shelf. According to the left-hand trajectories quality (see the 
video for the full motion) and path lengths, 9.10 (initial RRT-connect), 7.52 (RS), 
8.41 (PRS) and 2.70 (GB), the GB optimizer is the most successful in this case.

@@

% analysis PR2 alone:
In the example shown (Figure~\ref{pr2_final}) and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one, without any assumption about the group of DOF to activate (i.e. no DOF is locked). 
The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on the ground. Such behavior induces a high initial path length 
30.6. RS hardly optimizes the mobile base 
translation (Figure~\ref{pr2_final} middle) of the robot and other unnecessary DOF 
uses, resulting in a path length of 4.08.
Whereas the GB optimized-path mainly 
results in moving the arms as expected (Figure~\ref{pr2_final} right), just creating 
two collision-constraints between the arms. In the PRS 
result, only presented in the video, the mobile base motion is canceled. However, this is note the case for other unnecessary DOF motions. In addition, the arms motion is very wide and not as optimized as in the GB trajectory.

% analysis PR2 in kitchen:
We obtain similar results on the PR2 performing manipulation tasks 
in a kitchen environment.
Firstly, the robot moves its hands from the top to the bottom of a table.
The different trajectories of the right gripper are indicated in (Figure~\ref{fig:trajectories:kitchen1}).
Our optimizer manages to reduce the initial path length 12.7 from visibility-PRM 
and improves the path quality 
just adding constraints between the table and the 
robot's arms. Thus, the robot just slightly moves 
backward and uses its arms DOF to avoid the table, instead of 
processing a large motion to get away from the table. With the GB algorithm, the path length is 
reduced to 3.15, against 5.47 for RS.
Secondly, another example of PR2 going from the set to the fridge 
door is presented (Figure~\ref{fig:trajectories:kitchen2}) with the mobile base
trajectories. Here, GB and RS results are similar in terms of length and rendering.

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in (Table~\ref{tab:results}). In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case. 
On the one hand, for non-high DOF examples, it appears that computation time is higher using the GB 
optimization. The worst case comes out for the puzzle problem where the number of 
constraints of GB is significant and $\alpha_{init}$ reduced. 
In addition, collision checking is rapidly processed in such basic problem geometry. This favors RS while the GB optimizer spends time on the QP resolution to avoid collisions.
On the other hand, our method almost always provides the shortest paths, whereas it 
is not even the best criterion to quantify the parasite motions disappearance.
Note that these results are the consequence of the termination conditions of RS and PRS, balancing length reduction or shorter computation time. 
This is particularly visible for PRS which 
easily gives up in some problems, such as the 2D sliding-robot, the 
UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of (Table~\ref{tab:results}). 
Thus the issue addressed in (Figure~\ref{decoupled_DOF_optimization}) is 
solved considering this DOF.

>>>>

% one line version:
%Most algorithms in probabilistic sampling-based path planning compute collision-free paths made of straight line segments lying in the configuration space. Due to the randomness of sampling, the paths make detours that need to be optimized. The contribution of this paper is to propose a basic gradient-based (GB) algorithm that transforms a polygonal collision-free path into a shorter one. While requiring only collision checking, and not any time-consuming obstacle distance computation nor geometry simplification, we constrain only part of the configuration variables that may cause a collision, and not entire configurations. Thus parasite motions that are not useful for the problem resolution are reduced without any assumption. Experimental results include navigation and manipulation tasks, e.g. a manipulator arm filling boxes and a PR2 robot working in a kitchen environment. Comparisons with a random shortcut optimizer and a partial shortcut have also been studied.

@@

For this shortening purpose, random shortcut (RS) methods are
still very 
popular~\cite{Sekhavat-Svestka1998,Geraerts04clearancebased,HauserFastSmooth}. 
However, RS requires fine 
tuning of the termination condition and is no efficient for long 
trajectories where only a minor part needs to be optimized, 
as in Figure~\ref{local_box_optim}.
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS 
will always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs. This problem is 
addressed by our method.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building. For example,~\cite{HauserFastSmooth} returns smooth shortcuts made of parabola and line combinations, relying on the classical bang-bang control approach. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
Also based on random shooting,~\cite{Guernane2011} is guiding 
configuration-generation with local holonomic considerations. 
Nevertheless this method remains only 
locally optimal, and is not addressing high-DOF 
problems.~\cite{Geraerts04clearancebased} is 
using medial axis retraction for clearance and a PRS (shortcut is applied only 
on some random DOF) 
which can address the problem of Figure~\ref{decoupled_DOF_optimization}. 
However it is 
relatively slower than RS, and~\cite{Geraerts04clearancebased} only investigates 
it for freeflyer robots. 
Furthermore PRS is not taking advantage of information returned by 
the checker of which links are colliding, in order to guide the selection of a relevant group of DOF to shortcut.

In some way, our method shares similarities with~\cite{PanSmoothSplineShort} 
since this latter work relies on collision checking and backtracks when an 
iteration is detected in collision, instead of trying to constantly satisfy 
distance constraints. Unlike our method however, collision constraints are 
handled by interpolating configurations which, at some points of the trajectory, 
freeze the whole robot configuration instead of a pertinent subpart. Thus, this 
method cannot solve Figure~\ref{decoupled_DOF_optimization} issue.

@@

As illustrated in Figure~\ref{optim_grad}, let 
us denote by $\tcolli$ the abscissa of the first collision detected on path 
$\xx_{i+1}$, which previous iteration $\xx_i$ was collision-free. Thus in 
configuration $\xx_{i+1}(\tcolli)$ a collision has been 
detected. Two cases are possible:
\begin{enumerate}
\item the collision occurred between two bodies of the robot: $\body_1$ and $
\body_2$, or
\item the collision occurred between a body of the robot $\body_1$ and the 
environment.
\end{enumerate}
In the rest of this section, the first case will only be considered. Reasoning 
about the second case is similar, except that the 
constraint is on the position of $\body_1$ with respect to the environment.

@@

Therefore the following expressions
% \frac{\partial \conf}{\partial t}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \text{and} \ \frac{\partial \conf}{\partial t}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
\dot{\conf}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \ \text{and} \ \ \dot{\conf}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
correspond to $(\dot{\po_2}|\mathbf{u})$, respectively in configurations $\xx_{i}(t_{coll\ i})$ and $\xx_{i+1}(t_{coll\ i})$. The term $\dot{\conf}(1)$ being equal to zero requires either:
\begin {enumerate}
\item that $\po_1$ and $\po_2$ come to contact at zero velocity, or
\item the velocity of $\po_2$ in the reference frame of $\body_1$ is orthogonal to 
$\mathbf{u}$ at contact ($t=1$).
\end {enumerate}
The first case is very unlikely and almost never encountered in real applications, 
except if the user builds such a case on purpose.
The second case may appear and can be noted by a rank loss of $\Jf_{i+1}$.
Then we do not directly insert the new constraint. Instead, we process intermediate 
iterations until the redundancy vanishes, as explained in function 
\texttt{findNewConstraint} in (Algorithm~\ref{algo:solveRedundant}), and illustrated in Figure~\ref{fig:convergence-diagram}.

@@

Figure~\ref{2D_long} shows the result of our optimizer on 2D cases. Contact points which have 
led to constraints are represented. They permit to understand how the path is kept out of the obstacles. 
Unfortunately, it is not possible in the GB method to choose at which distance of the obstacle 
the constraint must be created, since at some parts the robot is very close to obstacles.

@@

Figure~\ref{local_box_optim} illustrates a \textit{very long} path example which RS 
or PRS will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. The GB method succeeds to optimize the 
path contained in the box, with the following cost coefficients:
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}, \  i \in [1\,..\, wp+1]  
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq wp+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated. This is not relevant for 
Figure~\ref{local_box_optim} type of problems where a local passage is very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper, and provides better quality results than the original cost.

@@

We also experiment our algorithm on more complex robots and environments.
In the included video and Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}, we present multiple situations where the GB algorithm 
is tested and compared to RS~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}) and PRS~\cite{partialrandomShortcutHPP} 
adapted from~\cite{Geraerts04clearancebased}.
The termination condition of RS allows it to try 
shortening the path until five iterations of non-improvement are reached. 
This corresponds to $maxNbFailures$ in (Algorithm~\ref{algo:random-shortcut}).
For our implementation of PRS, first a shortcut is tried on each DOF between 
$\conf_0$ and $\conf_{wp+1}$. 
Then, for each DOF, configurations are sampled as in 
(Algorithm~\ref{algo:random-shortcut}). The steering-method returns a path made of 
an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, we replace it as in RS. This process is also stopped when five 
iterations of non-improvement are reached.

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to Figure~\ref{fig:trajectories:puzzle}. The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
Lengths of initial, GB optimized, and RS optimized paths are 
respectively 23.4, 8.53 and 10.2. PRS fails to decrease the path length because in 
this problem, all DOF are closely related to cross the hole. This behavior was also 
noticed and improved in the PRS implementation of~\cite{Geraerts04clearancebased}, 
acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory 
even in the hole, contrary to RS which simply copies the initial path when the 
trajectory gets near of the obstacle. $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.

@@

% double-arm:
In the double-arm situation, Figure~\ref{fig:trajectories:double_arm}, one arm has 
to get around a cylinder obstacle while the 
other arm is relatively far from obstacles. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Unlike RS, 
the GB optimizer manages to cancel the rotation of the free-arm while optimizing the 
first arm motion, even if the second arm is still moving because of the translation 
motion. The initial path length 5.17 is decreased to 4.55 by RS, to 4.06 by PRS and 
to 2.77 by the GB method using three collision-constraints with the cylinder obstacle.

@@

% UR5-spheres:
Some problems are 
involving a 6-axis manipulator arm, also called UR5, equipped with a bar or a 
gripper.
In a relatively free environment represented in Figure~\ref{fig:trajectories:ur5}, 
results from our method and RS are similar (path length are respectively 2.03 and 1.60). 
Note also that the end-effector trajectory is completely different from the initial 
one: the robot is easily passing between the spheres, keeping its end-effector 
above.

% UR5-fiad
For an UR5 working in a cluttered environment inspired by an industrial issue 
Figure~\ref{fiad}, path optimization efficiently returns a shorter solution, close 
to the result of RS and to what can be observed in reality~\cite{factory-day-video}. 
The initial path length 6.65 is decreased to 2.08 by RS, to 
1.98 by the GB optimizer and unchanged by PRS.

% baxter:
A problem involving a Baxter-like\footnote{A torso rotation was added.} robot 
manipulating in an office environment is presented in
Figure~\ref{fig:trajectories:baxter}. The robot starts with its end-effectors 
above the computer and has to 
turn and reach the shelf. According to the left-hand trajectories quality (see the 
video for the full motion) and path lengths, 9.10 (initial RRT-connect), 7.52 (RS), 
8.41 (PRS) and 2.70 (GB), the GB optimizer is the most successful in this case.

@@

% analysis PR2 alone:
In the example shown Figure~\ref{pr2_final} and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one, without any assumption about the group of DOF to activate (i.e. no DOF is locked). 
The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on the ground. Such behavior induces a high initial path length 
30.6. RS hardly optimizes the mobile base 
translation (Figure~\ref{pr2_final} middle) of the robot and other unnecessary DOF 
uses, resulting in a path length of 4.08.
Whereas the GB optimized-path mainly 
results in moving the arms as expected (Figure~\ref{pr2_final} right), just creating 
two collision-constraints between the arms. In the PRS 
result, only presented in the video, the mobile base motion is canceled. However, this is not the case for other unnecessary DOF motions. In addition, the arms motion is very wide and not as optimized as in the GB trajectory.

% analysis PR2 in kitchen:
We obtain similar results on the PR2 performing manipulation tasks 
in a kitchen environment.
Firstly, the robot moves its hands from the top to the bottom of a table.
The different trajectories of the right gripper are indicated in Figure~\ref{fig:trajectories:kitchen1}.
Our optimizer manages to reduce the initial path length 12.7 from visibility-PRM 
and improves the path quality 
just adding constraints between the table and the 
robot's arms. Thus, the robot just slightly moves 
backward and uses its arms DOF to avoid the table, instead of 
processing a large motion to get away from the table. With the GB algorithm, the path length is 
reduced to 3.15, against 5.47 for RS.
Secondly, another example of PR2 going from the set to the fridge 
door is presented Figure~\ref{fig:trajectories:kitchen2} with the mobile base
trajectories. Here, GB and RS results are similar in terms of length and rendering.

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in (Table~\ref{tab:results}). In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case. 
On the one hand, for non-high DOF examples, it appears that computation time is higher using the GB 
optimization. The worst case comes out for the puzzle problem where the number of 
constraints of GB is significant and $\alpha_{init}$ reduced. 
In addition, collision checking is rapidly processed in such basic problem geometry. This favors RS while the GB optimizer spends time on the QP resolution to avoid collisions.
On the other hand, our method almost always provides the shortest paths, whereas it 
is not even the best criterion to quantify the parasite motions disappearance.
Note that these results are the consequence of the termination conditions of RS and PRS, balancing length reduction or shorter computation time. 
This is particularly visible for PRS which 
easily gives up in some problems, such as the 2D sliding-robot, the 
UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of (Table~\ref{tab:results}). 
Thus the issue addressed in Figure~\ref{decoupled_DOF_optimization} is 
solved considering this DOF.
